A Spatial AR System for Wide-area Axis-aligned Augmentation of Planar Scenes in Industrial Settings

### 2021-07-06 paper/elsarticle/elsarticle-template.tex
paper

\section{Hardware Setup}

@@

We evaluate our approach by augmenting 15 locations across the floorspace at the Pilotfabrik using our approach and two variants of a baseline approach. At each of the 15 locations, we aim to place an image aligned with the principal axes of the floorspace and such that the image appear in each instance to be free of projective distortions and to have the same dimensions, with the horizontal axis of the image as projected to the floor measuring 30 cm. We managed to carry out all steps using our approach within a time budget of 15 min. The first variant of the baseline approach is to carry out a manual keystone correction using the software bundled with the steerable mirror system mounted alongside our projector within the same 15 min time budget; we then compare the quality of the augmentations produced with this baseline with those produced using out approach. The second variant of the baseline approach is to record how much time is necessary to produce augmentations within a tolerance of what is desired.

>>>>

\section{Hardware Setup}\label{sec:hw}

@@

We evaluate our approach by augmenting 15 locations across the floorspace at the Pilotfabrik using our approach (`Our Approach') and two variants of a baseline approach (`Baseline A' and `Baseline B'). At each of the 15 locations, we aim to place an image aligned with the principal axes of the floorspace and such that the image appear in each instance to be free of projective distortions and to have the same dimensions (30 cm $\times{}$ 20 cm). Using our approach, we carried out all steps---which we further detail below---within a time budget of 15 min. Accordingly, we set 15 min to be the time budget of the first variant of the baseline approach (`Baseline A'), in which we carry out a \texit{manual} keystone correction using the software bundled with the steerable mirror system mounted alongside our projector (cf.\ Section~\ref{sec:hw}). We then compare the quality of the augmentations produced with this baseline with those produced using our approach. The second variant of the baseline approach (`Baseline B') is to record how much time is necessary to produce augmentations within a mean tolerance of 1 cm. All experiments were carried out by the same experienced technician and assistant.
